Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-05-08 automatica/paper.tex
added time out to Table 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Acrobot  & 4 &   &  &  &  & & & &\\
2  & Antenna  & 6 &   &  &  &  & & & &\\
3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & 24,14 & 425ms& 16,10 & 502ms\\
5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & 16,10 & 1398ms\\
6  & Chen\_ex2 & 8& & & 32,23 & 4683872ms &  & & &\\
7  & Chen\_ex3 & 7 &   & & & & & & &\\
8  & Chen\_ex4 & 9 &  & & & & & & &\\
9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms & 24,14 & 295ms& 16,10 & 306ms\\
10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  24,14 &293ms& 16,10 & 313ms\\
11 & Cstr & 1 & &  & & & & & &\\
12 & Cstrtmp  & 1 &   &  & & & 24,14 &478ms& &\\
13 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & 24,14 & 435ms& 16,10 & 520ms\\
14 & Flexbeam   & 6 &   &  & & & 24,14 &72079ms& &\\
15 & Guidance chen  & 5 &   &  & & & & & &\\
16 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & 24,14 & 727ms& 16,10 &1075ms\\
17 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
18 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & 24,14 & 432ms& 16,10 &466ms\\
19 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & 24,14  & 916ms& 16,10 &1244ms\\
20 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & 24,14 & 443ms & 16,10 &569ms\\
21 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & 24,14 & 395ms& 16,10 &473ms\\
22 & Regulator   & 5 &   &  & & & & & &\\
23 & Springmassdamper & 2 &   &  & & & & & &\\
24 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & 24,14 & 701ms& 16,10 &1225ms\\
25 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & 56,30 & 15268ms& 16,10 &4374ms\\
26 & Tapedriver   & 3 & 16,8  & 8188ms & & & 64,22 & 2026ms& 16,10 &1090ms\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}

>>>>

For the majority of our benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds one solution more (9) than the multi-staged back-end (8).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 70\% of the time required using the multi-staged
back-end, and has a median run-time 1.4\,s, which is seven times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve all benchmarks in the set.  On average
our engine spent 52\% in the synthesis and 48\% in the verification phase.

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Acrobot  & 4 &  & \xmark &  & ~\xmark & & ~\xmark &  & ~\xmark \\
2  & Antenna  & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
4  & Bioreact & 3 & 16,8 & 11.2\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
5  & Chen\_ex1& 3 & 16,8 & 7.2\,s  & 16,10 & 9.2\,s & & ~\xmark & 16,10 & 1.4\,s\\
6  & Chen\_ex2 & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
7  & Chen\_ex3 & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
8  & Chen\_ex4 & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
9  & Cruise    & 1 & 16,8 & 6.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
10 & CruiseHSCC & 1 & 16,8 & 6.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
11 & Cstr & 1 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
12 & Cstrtmp  & 1 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
13 & DCmotor   & 2 & 16,8  & 6.9\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s \\
14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s\\
17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s\\
20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s\\
21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
22 & Regulator   & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\
25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s\\
26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 16,10 & 1.1\,s\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}
